\documentclass[a4paper,10pt]{article}

% Set page margins
\usepackage[scale=0.875]{geometry}

\usepackage[hidelinks]{hyperref}


% Remove page numbering
\pagestyle{empty}

% Define custom commands for sections
\newcommand{\resumeSection}[1]{\vspace{2pt}\noindent{\Large \textbf{#1}}\vspace{1pt}\newline}
\newcommand{\resumeSubsection}[2]{\noindent\textbf{#1} \hfill #2\newline}

\begin{document}

\begin{center}
    {\LARGE \textbf{Jacob Johnson}} \\
    \vspace{2pt}
    +1 (801) 824-2215  | jacob@nnnNNnnn.info
\end{center}

\resumeSection{Overview}
    \indent I am a Computer Engineering student interested in a career in hardware/embedded systems design. I am familiar with VHDL and assembly development. I consider myself most fluent in Python, including the NumPy library, due to my academic history in Natural Language Processing/Artificial Intelligence, but I have also used Java, C\#, and C. I proudly contributed to five academic publications across the fields of Linguistics and Natural Language Processing during my undergrad and my one-year stint in a PhD program; these are listed below. I am currently completing leveling courses towards my Master's Degree and will resume taking graduate-level courses this Spring. I speak German proficiently and Spanish at a beginner level. \\


\resumeSection{Education}
    \resumeSubsection{M.S., Computer Engineering (GPA 4.0)}{Weber State University, Fall 2024 - Spring 2027}
        %Cumulative GPA of 4.0 \\
        Courses Include: ECE 3610 ``Digital Systems'', ECE 3710 ``Embedded Systems'', ECE3210 ``Signals and Systems'' \\
        Planned (Spring 2026) Courses Include: ECE 6210 ``Digital Signal Processing''\\
        Recipient of an \textit{ECE Department Service Scholarship} for implementing homeworks into an in-house online LMS. \\
    \resumeSubsection{Incomplete Ph.D., Computer Science (GPA 4.0)}{University of Utah, Fall 2023 - Spring 2024}
        Ended the program early to change topic of interest \\
        %Cumulative GPA of 4.0 \\
        Courses Include: CS 6350 ``Machine Learning'', CS 6150 ``Graduate Algorithms'' \\
    \resumeSubsection{B.A., Linguistics + Computer Science Minor (GPA 4.0)}{University of Utah, Spring 2020 - Spring 2023}
        \textit{University of Utah College of Humanities Research Award} and \textit{Allan A \& Renee Wright Hagander Book Award} recipient\\
        %Cumulative GPA of 4.0 \\
        Courses Include: CS 5340 ``Natural Language Processing'', CS 6390 ``Information Extraction (from text)'', LING 5300 ``Computational Linguistics'', CS 6353 ``Deep Learning'' \\


\resumeSection{Work Experience}
    \resumeSubsection{Math/CS tutor for Athletes at Weber State University (20hrs/wk)}{August 2025 -- Present}
        \indent I tutor student atheletes on topics in Math/Computer Science courses. \\
    \resumeSubsection{Cashier at Smiths Food and Drug (40hrs/wk)}{August 2024 -- Present}
        \indent I manage a self checkout aisle and assist customers. \\
    \resumeSubsection{Training Data Labeling Intern at FamilySearch (20hrs/wk)}{May 2024 -- August 2024}
        \indent I meticulously labeled detailed historical documents for use in AI training. \\
    \resumeSubsection{Research Assistant at University of Utah (40+hrs/wk)}{May 2023 -- May 2024}
        \indent I researched NLP with local and remote colleagues and published one paper on my findings. \\
    \resumeSubsection{Teaching Assistant at University of Utah (20hrs/wk)}{August 2021 -- May 2023}
        \indent I taught students in a range of undergrad/grad CS courses through labs, feedback, and help hours. \\
    \resumeSubsection{Assistant Aquatics Director at Camp Tifie, BSA (40+hrs/wk)}{June 2021 - July 2021}
        \indent I maintained pool equipment and supplies, taught swimming and water rescue skills, and lifeguarded. \\
    \resumeSubsection{Production+Picking Team Member at Loftus International (40hrs/wk)}{May 2020 -- March 2021}
        \indent I assembled products and prepared orders for shipping. \\
    \resumeSubsection{SolidWorks Designer at Epiroc (10hrs/wk)}{November 2019 -- April 2020}    
        \indent I designed and modeled mining drills in SolidWorks CAD format. \\
    \resumeSubsection{SolidWorks Designer and Machinist at Clean Machine (40hrs/wk)}{January 2016 -- September 2017}
        \indent I translated paper drawings of acquired IP into SolidWorks CAD format and operated CNC mills and lathes. \\



\resumeSection{Academic Publications}
    \textit{{\href{https://www.iastatedigitalpress.com/psllt/article/id/18429/}{``An Investigation of the Relationship Between Perceptual Sensitivity and Word Learning Performance for the Hindi Voiced Unaspirated Dental-Retroflex Contrast by English Speakers'' (PSLLT 2024)}}}
        - I contributed to developing the participant interface for online data collection in the preliminary experiments\\
    \textit{{\href{https://aclanthology.org/2024.scil-1.23/}{``Online Learning of ITSL Grammars'' (SCiL 2024)}}}
        - I developed, implemented, and evaluated an algorithm for learning ITSL languages\\
    \textit{{\href{https://aclanthology.org/2023.blackboxnlp-1.19/}{``How much Consistency is your Accuracy Worth?'' (BlackBoxNLP@EMNLP2023)}} }
        - I developed a measurement to compare consistency of AI models' at different levels of accuracy. \\
    \textit{\href{https://scholarworks.umass.edu/cgi/viewcontent.cgi?article=1268\&context=scil}{``Evaluating a Phonotactic Learner for MITSL-(2,2) Languages'' (SCiL 2023)}} 
        - I implemented and evaluated the {MITSL2IA learning algorithm} for learning MITSL$_2^2$ languages\\
    \textit{{\href{{https://www.cambridge.org/core/journals/studies-in-second-language-acquisition/article/effects-of-exposure-and-explicit-stereotypes-on-veracity-judgments-of-polishaccented-english-speech-a-preregistered-close-replication-and-extension-of-boduchgrabka-levari-2021/EF03B7A762B1442206B537F0AD4447A4}}{``The Effects of Exposure and Explicit Stereotypes on Veracity Judgments of Polish-Accented English Speech: A Replication and Extension of Boduch-Grabka \& Lev-Ari (2021)''}}} 
        -I substantially contributed to developing the participant interface for data collection in an online study

%\resumeSection{Technology-Relevant Personal Experience}
%    I run a home server and self-host/maintain an Immich photo server, a Minecraft server and have hosted several custom web servers. \\
%    I set up a fleet of laptops for use by the charity Nurturing Nations at a school and library in Ghana. \\
%    I have built my own PC and have performed repairs and upgrades on my own laptops and those of my friends and family. \\

\end{document}
