\documentclass[a4paper,10pt]{article}

% Set page margins
\usepackage[scale=0.8]{geometry}

\usepackage[hidelinks]{hyperref}


% Remove page numbering
\pagestyle{empty}

% Define custom commands for sections
\newcommand{\resumeSection}[1]{\vspace{2pt}\noindent{\Large \textbf{#1}}\vspace{1pt}\newline}
\newcommand{\resumeSubsection}[2]{\noindent\textbf{#1} \hfill #2\newline}

\begin{document}

\begin{center}
    {\LARGE \textbf{Jacob Johnson}} \\
    \vspace{2pt}
    +1 (801) 824-2215  | jacob@nnnNNnnn.info
\end{center}

\resumeSection{Overview}
    Fluent in Python, proficient with NumPy library, familiar with Flask library \\
    Familiar with VHDL, Java, C\#, HTML and assembly \\
    Native English Speaker, Proficient at German, Basic Spanish \\

\resumeSection{Work Experience}
    \resumeSubsection{Cashier at Smiths Food and Drug (40hrs/wk)}{August 2024 -- Present}
        I manage a self checkout aisle and assist customers. \\
    \resumeSubsection{Training Data Labeling Intern at FamilySearch (20hrs/wk)}{May 2024 -- August 2024}
        I meticulously labeled detailed historical documents for use in AI training. \\
    \resumeSubsection{Research Assistant at University of Utah (40+hrs/wk)}{May 2023 -- May 2024}
        I researched NLP with local and remote colleagues and published one paper on my findings. \\
    \resumeSubsection{Teaching Assistant at University of Utah (20hrs/wk)}{August 2021 -- May 2023}
        I taught students in a range of undergrad/grad CS courses through labs, feedback, and help hours. \\
    \resumeSubsection{Assistant Aquatics Director at Camp Tifie, BSA (40+hrs/wk)}{June 2021 - July 2021}
        I maintained pool equipment and supplies, taught swimming and water rescue skills, and lifeguarded. \\
    \resumeSubsection{Production+Picking Team Member at Loftus International (40hrs/wk)}{May 2020 -- March 2021}
        I assembled products and prepared orders for shipping. \\
    \resumeSubsection{SolidWorks Designer at Epiroc (10hrs/wk)}{November 2019 -- April 2020}    
        I designed and modeled mining drills in SolidWorks CAD format. \\
    \resumeSubsection{SolidWorks Designer and Machinist at Clean Machine (40hrs/wk)}{January 2016 -- September 2017}
        I translated paper drawings of acquired IP into SolidWorks CAD format and operated CNC mills and lathes. \\

\resumeSection{Education}
    \resumeSubsection{M.S., Computer Engineering}{Weber State University, Fall 2024 - Spring 2027}
        Cumulative GPA of 4.0 \\
        Courses Include: ECE 3610 ``Digital Systems'', ECE 3710 ``Embedded Systems'' \\
    \resumeSubsection{Incomplete Ph.D., Computer Science}{University of Utah, Fall 2023 - Spring 2024}
        Ended the program early to change topic of interest \\
        Cumulative GPA of 4.0 \\
        Courses Include: CS 6350 ``Machine Learning'', CS 6150 ``Graduate Algorithms'' \\
    \resumeSubsection{B.A., Linguistics + Computer Science Minor}{University of Utah, Spring 2020 - Spring 2023}
        Cumulative GPA of 4.0 \\
        Courses Include: CS 5340 ``Natural Language Processing'', CS 6390 ``Information Extraction (from text)'', LING 5300 ``Computational Linguistics'', CS 6353 ``Deep Learning'' \\

\resumeSection{Academic Publications}
    \textit{{\href{https://aclanthology.org/2024.scil-1.23/}{``Online Learning of ITSL Grammars'' (SCiL 2024)}}}
        - I developed, implemented, and evaluated an algorithm for learning ITSL languages\\
    \textit{{\href{https://aclanthology.org/2023.blackboxnlp-1.19/}{``How much Consistency is your Accuracy Worth?'' (BlackBoxNLP@EMNLP2023)}} }
        - I developed a measurement to compare consistency of AI models' at different levels of accuracy. \\
    \textit{\href{https://scholarworks.umass.edu/cgi/viewcontent.cgi?article=1268\&context=scil}{``Evaluating a Phonotactic Learner for MITSL-(2,2) Languages'' (SCiL 2023)}} 
        - I implemented and evaluated the {MITSL2IA learning algorithm} for learning MITSL$_2^2$ languages\\
    \textit{{\href{{https://www.cambridge.org/core/journals/studies-in-second-language-acquisition/article/effects-of-exposure-and-explicit-stereotypes-on-veracity-judgments-of-polishaccented-english-speech-a-preregistered-close-replication-and-extension-of-boduchgrabka-levari-2021/EF03B7A762B1442206B537F0AD4447A4}}{``The Effects of Exposure and Explicit Stereotypes on Veracity Judgments of Polish-Accented English Speech: A Replication and Extension of Boduch-Grabka \& Lev-Ari (2021)''}}} 
        -I substantially contributed to developing the interface for data collection in an online study\\

\resumeSection{Technology-Relevant Personal Experience}
    I run a home server and self-host/maintain an Immich photo server, a Minecraft server and have hosted several custom web servers. \\
    I set up a fleet of laptops for use by the charity Nurturing Nations at a school and library in Ghana. \\
    I have built my own PC and have performed repairs and upgrades on my own laptops and those of my friends and family. \\

\end{document}
